\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb,amsmath}
\usepackage{hyperref}
%SetFonts

%SetFonts


\title{Deciphering SUGAR}
\author{Alex Kim}
%\date{}							% Activate to display a given date or no date

\begin{document}
\section{The Model}
\url{https://arxiv.org/pdf/1909.11239.pdf}

For supernova $i$, Equations 22-25
\begin{align*}
M_i &= M_0(t,\lambda) + \sum_j h_{ij} \alpha_j(t,\lambda) + A_{V,i} \gamma+ \Delta M_{i, grey}
\end{align*}
Note that $\gamma$ is used in place of $ f(\lambda, R_V)$.

In our analysis we don't treat the extinction separately.
\begin{align*}
M_i &= M_0(t,\lambda) + \sum_j h_{ij} \alpha_j(t,\lambda) + \Delta M_{i, grey}
\end{align*}
but we are setting $\alpha_1$, $\alpha_2$ to be time independent, as dust would be.

\section{Degeneracies in the Model}
\subsection{$h$ and $\alpha$}
There is the invariance  between $h$ and $\alpha$.  Introducing $c_j$
\begin{align*}
 h_{ij} &\rightarrow  h_{ij} c_j\\
 \alpha_j  & \rightarrow  \alpha_j/c_j.
\end{align*}
This degeneracy is fixed by making each $\alpha_j$ a unit vector.

An alternative way to fix this degeneracy is to set $c_j = 1/\text{s.d.}(h_{xj})$.

Neither of the above solutions fix the $\pm$ sign.  A solution is for each $j$
identify the $h_{ij}$ that has the highest signal-to-noise, and if it is reasonable
assign it to be positive (or negative).



\subsection{$h$ and $M_0$}
There is the invariance  between $h$ and $M_0$.  Introducing $c_j$
\begin{align*}
 h_{ij} &\rightarrow  h_{ij} + c_j\\
 M_0 & \rightarrow  M_0 - c_j \alpha_j.
\end{align*}
This degeneracy is fixed by setting $c_j = -\langle h_{xj} \rangle$.

\subsection{$h$ and $\Delta M$}
This is a special case of the  invariance  between $h$ and $M_0$.
\begin{align*}
 \Delta M_{i, grey} &\rightarrow  \Delta M_{i, grey} + c\\
 M_0 & \rightarrow  M_0 - c
\end{align*}
This degeneracy is fixed by setting $c = -\langle \Delta M \rangle$.

\subsection{$\Delta M$ and $\alpha$}
There is the invariance  between the grey term and $\alpha$.  Introducing $c_j$
\begin{align*}
 \Delta M_{i, grey} &\rightarrow \Delta M_{i, grey}  + \sum_j h_{ij} c_j  \\
 \alpha_j  & \rightarrow  \alpha_j  - c_j.
\end{align*}
For physical reasons we want $\Delta M_{i, grey}$ to be uncorrelated with the $h_{ij}$.
This is achieved by 
\begin{equation}
c = [\text{cov}(h)]^{-1} \text{cov}(h,\Delta M_{grey}).
\end{equation}



\end{document}  